### 2023-09-06 3.Design/activation.tex
Gros pc pas commits...

@@

The circuit used is the same as the one in \cite{thesisRef}, the circuit is the one shown in figure \ref{fig:afCircuit}. The technology used being different, all the parameters had to be determined empirically to best fit a sigmoid shape. The parameters can be found in ( TODO : show af parameters ).

@@

This circuit outputs a voltage that depends on the input voltage passed on. The relation between the two is shown in figure

>>>>

\begin{table}[H]
  \centering
  \caption{Circuits parameters}
  \begin{tabular}{|c|c|c|}
    \hline
    \rowcolor{gray}
    Parameter & Sigmoid & \ac{tanh} \\
    \hline
    $V_1$ & \multicolumn{2}{c|}{$1.1V$}\\
    \hline
    $V_2$ & \multicolumn{2}{c|}{$635mV$}\\
    \hline
    $V_3$ & $0.8V$ & $550mV$\\
    \hline
    $i_{dc}$ & \multicolumn{2}{c|}{$150uA$}\\
    \hline
    $w$ & \multicolumn{2}{c|}{$900nm$}\\
    \hline
    $l$ & \multicolumn{2}{c|}{$60nm$}\\
    \hline
    $R_1$ & \multicolumn{2}{c|}{$5k\Omega$}\\
    \hline
    $R_2$ & \multicolumn{2}{c|}{$10k\Omega$}\\
    \hline
    $R_3$ & $2k\Omega$ & $4k\Omega$\\
    \hline
  \end{tabular}
  \label{tab:afPar}
\end{table}

@@

The circuit used is the same as the one in \cite{thesisRef}, the circuit is the one shown in figure \ref{fig:afCircuit}. The technology used being different, all the parameters had to be determined empirically to best fit a sigmoid shape. The parameters can be found in table \ref{tab:afPar}.

@@

This circuit outputs a voltage that depends on the input voltage passed on. The relation between the two is shown in figure. %TODO

Note that the actual output of the circuit in figure \ref{fig:afCircuit} is inverted arround $V_{cm}$ a simple circuit such as the one shown in  (TODO show circuit in annex) does inverts the
